\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{amsmath}
\usepackage[hmargin=3cm,vmargin=6.0cm]{geometry}

%\topmargin=0cm
\topmargin=-2cm
\addtolength{\textheight}{6.5cm}
\addtolength{\textwidth}{2.0cm}
%\setlength{\leftmargin}{-5cm}
\setlength{\oddsidemargin}{0.0cm}
\setlength{\evensidemargin}{0.0cm}

%misc libraries goes here

\begin{document}

\section*{Student Information } 
%Write your full name and id number between the colon and newline
%Put one empty space character after colon and before newline
Full Name : Mithat Can Timurcan \\
Id Number :  2581064\\

% Write your answers below the section tags
\section*{Answer 1}

\subsection*{a)} 
\begin{itemize}
    \item In order to obtain a 95\% confidence interval for our normally distributed sample, we need to use the according $z$ value $z_{\alpha/2}$. Since $1-\alpha$ is given as 0.95, $\alpha$ becomes 0.05 and our according $z$ value becomes $z_{0.025}$ which is 1.96.
    \item While obtaining a confidence interval we use the following formula:
    \begin{equation*}
        \begin{split}
            \overline{X} \pm z_{\alpha/2} \cdot \dfrac{\sigma}{\sqrt[]{n}}
        \end{split}
    \end{equation*}
    \item We can find our mean value $\overline{X}$ by doing the following:
    \begin{equation*}
        \begin{split}
            \overline{X} = \dfrac{\sum_{i = 1}^{n} X_i}{n} = \dfrac{6.4 + 9.5 + 8.2 + 10.2 + 7.6 + 11.1 + 8.7 + 7.3 + 9.1}{9} \approx 8.68
        \end{split}
    \end{equation*}
    \item Let's put our values, $\overline{X} \approx 8.68$, $n = 9$, $\sigma = 2.7$, $z_{\alpha/2} = z_{0.025} = 1.96$:
    \begin{equation*}
        \begin{split}
            \overline{X} \pm z_{\alpha/2} \cdot \dfrac{\sigma}{\sqrt[]{n}} = (8.68) \pm (1.96) \cdot \dfrac{(2.7)}{\sqrt[]{9}} = [6.91,10.44]
        \end{split}
    \end{equation*}
\end{itemize}

\subsection*{b)} 
\begin{itemize}
    \item In order to find the size that we need to obtain a specific margin, we use the following:
    \begin{equation*}
        \begin{split}
            \Delta = z_{\alpha/2} \cdot \dfrac{\sigma}{\sqrt[]{n}} \ \rightarrow \ n \geq { \left(\frac{z_{\alpha/2} \cdot \sigma}{\Delta}\right) }^2
        \end{split}
    \end{equation*}
    \item Again, putting our values $\sigma = 2.7$, $z_{\alpha/2} = z_{0.025} = 1.96$ and $\Delta = 1.25$ we get:
    \begin{equation*}
        \begin{split}
            n \geq { \left(\frac{z_{\alpha/2} \cdot \sigma}{\Delta}\right) }^2 = { \left(\frac{1.96 \cdot 2.7}{1.25}\right) }^2 = 17.92 \approx 18
        \end{split}
    \end{equation*}
    \item Therefore, our sample size should be more than 18 so that we can get a margin maximum of 1.25.
\end{itemize}



\section*{Answer 2}

\subsection*{a)} 
\begin{itemize}
    \item Since we want to test if their average revenue has increased or not, we can set up the hypotheses as follows:
    \begin{equation*}
        \begin{split}
            H_0: \mu = 20000 \\
            H_A: \mu > 20000
        \end{split}
    \end{equation*}
    \item In this case, Mecnun's claim will be the null hypothesis $H_0$ and Leyla's claim will be the alternative hypothesis $H_A$.
\end{itemize}

\subsection*{b)}
\begin{itemize}
    \item In order to test our statistics with a 5\% level of significance, we'll use a right-tail $z$-test with the according $z$ value:
    \begin{equation*}
        \begin{split}
            \alpha = 0.05 \ \rightarrow \ z_\alpha = z_{0.05} = 1.645 \\
            \begin{cases}
                \ \text{accept $H_0$} \quad \text{if} \quad Z < 1.645\\
                \ \text{reject $H_0$} \quad \text{if} \quad Z \geq 1.645\\
            \end{cases}
        \end{split}
    \end{equation*}
    \item Now we need to compute our $Z$ value and check if it's in the accepted region:
    \begin{equation*}
        \begin{split}
            Z = \dfrac{\overline{X} - \mu_0}{\sigma \ / \ \sqrt[]{n}} = \dfrac{22000 - 20000}{3000 \ / \ \sqrt[]{50}} \approx 4.71
        \end{split}
    \end{equation*}
    \item Since $Z = 4.71$ is in the rejected region, we will reject the null hypothesis. The data provided supports the conclusion that there is a significant increase in the average amount of revenue.
\end{itemize} 

\subsection*{c)} 
\begin{itemize}
    \item Since we've found our observed $Z$ value, we can compute the p-value for Mecnun's test by using \texttt{normcdf(Z)}:
    \begin{equation*}
        \begin{split}
            P = \textbf{P}\{Z \geq Z_{obs}\} = \textbf{P}\{Z \geq 4.71\} = 1 - \Phi(4.71) \approx 0.000\\
        \end{split}
    \end{equation*}
    \item Since we got an extremely low p-value, we have grounds to reject the null hypothesis not just at the 5\% significance level asked in the question, but also at the 1\% and even the 0.05\% levels.
\end{itemize}

\subsection*{d)} 
\begin{itemize}
    \item In order to test if their average revenue is higher than the competitor's value, we should set up the hypotheses as follows:
    \begin{equation*}
        \begin{split}
            H_0: \mu_X - \mu_Y = 0 \\
            H_A: \mu_X - \mu_Y > 0
        \end{split}
    \end{equation*}
    \item Then, we should find the acceptance region for the right-tail $z$-test with 1\% significance:
    \begin{equation*}
        \begin{split}
            \alpha = 0.01 \ \rightarrow \ z_\alpha = z_{0.01} = 2.32 \\
            \begin{cases}
                \ \text{accept $H_0$} \quad \text{if} \quad Z < 2.32\\
                \ \text{reject $H_0$} \quad \text{if} \quad Z \geq 2.32\\
            \end{cases}
        \end{split}
    \end{equation*}
    \item Let's compute our $Z$ value and check if it's in the accepted region:
    \begin{equation*}
        \begin{split}
            Z = \dfrac{\overline{X} - \overline{Y}}{\sqrt[]{\dfrac{\sigma_X^2}{n} + \dfrac{\sigma_Y^2}{m}}} = \dfrac{22000 - 24000}{\sqrt[]{\dfrac{(3000)^2}{50} + \dfrac{(4000)^2}{40}}} \approx -2.62
        \end{split}
    \end{equation*}
    \item Since $Z = -2.62$ is not in the rejected region, we can't reject the null hypothesis. Therefore with \%1 significance, we can't claim that Leyla and Mecnun's average revenue is higher than the competitor's average revenue.
\end{itemize}


\section*{Answer 3}
\begin{itemize}
    \item We are given the observed table, let us put the values:
    \begin{table}[H]
        \small
        \centering
        \begin{tabular}{|c|c|c|c|c|c|c|}
        \hline
        $Obs(i,j) = n_{ij}$ & Black Coffee & Coffee with Milk & Coffee with Sugar & $n_{i.}$ \\
        \hline
        Male & 52 & 16 & 32 & 100\\
        Female & 17 & 63 & 20 & 100\\
        \hline
        $n_{.j}$ & 69 & 79 & 52 & 200\\
        \hline
        \end{tabular}
    \end{table}
    \item We are going to test the following hypotheses:
    \begin{equation*}
        \begin{split}
            H_0: \text{Gender and choice of coffee are independent factors.} \\
            H_A: \text{Gender and choice of coffee are dependent factors.}
        \end{split}
    \end{equation*}
    \item Now let us compute the estimated expected values:
    \begin{equation*}
        \begin{split}
            \widehat{Exp}(i,j) = \frac{n_{i.} \cdot n_{.j}}{n} \\
        \end{split}
    \end{equation*}
    \begin{equation*}
        \begin{split}
            \widehat{Exp}(1,1) = \frac{69 \cdot 100}{200} = 34.5 \quad \quad \widehat{Exp}(2,1) = \frac{69 \cdot 100}{200} = 34.5 \\ \\
            \widehat{Exp}(1,2) = \frac{79 \cdot 100}{200} = 39.5 \quad \quad \widehat{Exp}(2,2) = \frac{79 \cdot 100}{200} = 39.5 \\ \\
            \widehat{Exp}(1,3) = \frac{52 \cdot 100}{200} = 26 \quad \quad \widehat{Exp}(2,3) = \frac{52 \cdot 100}{200} = 26 \\ \\
        \end{split}
    \end{equation*}
    \begin{table}[H]
        \small
        \centering
        \begin{tabular}{|c|c|c|c|c|c|c|}
        \hline
        $\widehat{Exp}(i,j) = \frac{n_{i.} \cdot n_{.j}}{n}$ & Black Coffee & Coffee with Milk & Coffee with Sugar & $n_{i.}$ \\
        \hline
        Male & 34.5 & 39.5 & 26 & 100\\
        Female & 34.5 & 39.5 & 26 & 100\\
        \hline
        $n_{.j}$ & 69 & 79 & 52 & 200\\
        \hline
        \end{tabular}
    \end{table}
    \item We can compute our chi-square value:
    \begin{equation*}
        \begin{split}
            {\chi_{obs}}^2 = \sum_{i = 1}^k\sum_{j = 1}^m \frac{\{ Obs(i,j) - \widehat{Exp}(i,j)\}^2 }{\widehat{Exp}(i,j)}
        \end{split}
    \end{equation*}
    \begin{equation*}
        \begin{split}
            {\chi_{obs}}^2 = \frac{(52 - 34.5)^2}{34.5} + \frac{(17 - 34.5)^2}{34.5} + \frac{(16 - 39.5)^2}{39.5} + \frac{(63 - 39.5)^2}{39.5} + \frac{(32 - 26)^2}{26} + \frac{(20 - 26)^2}{26}\\
            \approx 48.5
        \end{split}
    \end{equation*}
    \item From Table A6, with the degrees of freedom $(3-1)(2-1) = 2$, we find that the p-value $P < 0.001$ and therefore, we reject the null hypothesis. We have a significant evidence that gender is related to the coffee choice.
\end{itemize}


\end{document}
